\section{Requirements from Stakeholders}

\subsection{Operations Manager (Lara, 24)}

\begin{quote}
    “We often run out of ingredients like oat milk and vanilla syrup. I'd love a dashboard where I can see the inventory level. Also, combo offers like 'Coffee \& Croissant' must be treated as one product.”
\end{quote}

\begin{quote}
    “I need a shopping list that includes all ingredience that we are running low on. This shopping list should be automatically managed.”
\end{quote}

\begin{quote}
    “Our coffee comes in 3 sizes: Small, Medium and Large. Tea is always medium.”
\end{quote}

\subsection{Head Barista (Nico, 29)}

\begin{quote}
    “When customers ask about ingredients or allergens, I flip through a laminated folder. We need a system where I can quickly see if a product contains nuts or gluten.”
\end{quote}

\begin{quote}
    “Whenever I train a new employee, it takes a lot of time to teach them every drink and how to prepare it. It would be nice to have an enumerated list with steps for every drink - just like a recipe.”
\end{quote}

\subsection{Barista (Lilli, 17)}

\begin{quote}
    “I am here quite rarely AND I don't drink tea. I need to know how hot the water should be for every tea flavour and it should not be that complicated to see that.”
\end{quote}

\begin{quote}
    “We serve coffee, tea and a small assortment of baked goods.”
\end{quote}

\subsection{Customer Loyalty Lead (Tariq, 21)}

\begin{quote}
    “I’m running a student thesis about personalized offers. We should track customer preferences and how often they buy their favorite drink.”
\end{quote}

\begin{quote}
    “A lot of customers ask for stamp cards. We might want to provide a virtual stamp card connected to every customer. After 9 coffees, the 10th is on the house!”
\end{quote}

\subsection{Finance Assistant (Dr. Mai, 46)}

\begin{quote}
    “We calculate revenue manually at the end of the day. It would be great to extract a report with total sales per product and daily revenue.”
\end{quote}

\begin{quote}
    “We will lose a lot of money if every customer gets a stamp card from the start. They should ask us - and then they get their first stamp on their virtual card.”
\end{quote}

\begin{quote}
    “There are no prices as for now. We plan on changing our whole price structure. A small basic coffe will be 1 euro and everything else will be a bit more expensive. A medium coffee will be 50 percent more and a large one will be 100 percent more expensive.”
\end{quote}